---
output: github_document
editor_options:
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
if (!interactive()) {
  options(width = 99)
}
```

# ifc

<!-- badges: start -->
[![Lifecycle: experimental][life_badge]][life_link]
[![CRAN status][cran_badge]][cran_link]
[![Codecov test coverage][cov_badge]][cov_link]
[![R build status][ga_badge]][ga_link]
<!-- badges: end -->

The ifc package implements the [International Fixed Calendar][ifc_wiki] as a
proper S3 vector class. The IFC divides each year into 13 months of exactly 28
days, with a Year Day appended at year's end (and a Leap Day after IFC June 28
in leap years). Because each month always starts on Sunday and ends on Saturday,
the day-of-week for any IFC date is fully deterministic from the day-of-month
number.

## Installation

Install the development version from [GitHub][gh]:

```{r install, eval=FALSE}
# install.packages("pak")
pak::pak("k5cents/ifc")
```

## Usage

```{r usage}
library(ifc)
library(tibble)

# Convert from Gregorian
ifc_date("2024-06-18")

# Construct from IFC components (Sol 1, 2024)
ifc_ymd(2024, 7, 1)

# Intercalary days
ifc_year_day(2024)
ifc_leap_day(2024)
```

```{r accessors}
x <- ifc_ymd(2024, 7, 14)

ifc_year(x)
ifc_month(x)   # 7 = Sol
ifc_day(x)
ifc_wday(x, label = TRUE)  # deterministic: day 14 = Saturday
```

```{r format}
format(x, "%B %d, %Y")
format(x, "%a %B %d")
```

```{r tibble}
firsts <- seq(as.Date("2025/1/1"), by = "month", length.out = 12)
tibble(
  gregorian = firsts,
  fixed = ifc_date(gregorian)
)
```

## Code of Conduct

Please note that the ifc project is released with a
[Contributor Code of Conduct][coc]. By contributing to this project, you agree
to abide by its terms.

<!-- links -->
[ifc_wiki]: https://en.wikipedia.org/wiki/International_Fixed_Calendar
[gh]: https://github.com/k5cents/ifc
[coc]: https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html

[life_badge]: https://img.shields.io/badge/lifecycle-experimental-orange.svg
[life_link]: https://lifecycle.r-lib.org/articles/stages.html#experimental
[cran_badge]: https://www.r-pkg.org/badges/version/ifc
[cran_link]: https://CRAN.R-project.org/package=ifc
[cov_badge]: https://codecov.io/gh/k5cents/ifc/graph/badge.svg
[cov_link]: https://app.codecov.io/gh/k5cents/ifc
[ga_badge]: https://github.com/k5cents/ifc/actions/workflows/R-CMD-check.yaml/badge.svg
[ga_link]: https://github.com/k5cents/ifc/actions/workflows/R-CMD-check.yaml
